This appendix describes the 16 BEAR corpora used in the paper. The full
BEAR database contains additional datasets documented elsewhere.

\newpage

\subsection{psymetadata and Nuijten et al (psychology
datasets)}\label{psymetadata-and-nuijten-et-al-psychology-datasets}

\textbf{Reference:} Set of psychology datasets compiled by
\textcite{rodriguez2022psymetadata}. We also disaggregate a large
meta-meta-analysis of intelligence research
\autocite{nuijten2020intelligence}.

\textbf{Snapshot date:} Jan 2026

\textbf{Research question:} \emph{psymetadata} is an R package that
curates multiple open datasets from published meta-analyses in
psychology for teaching and demonstrations.
\textcite{nuijten2020intelligence} is a large meta-meta-analysis of
intelligence research, which focused on power and small study effects.

\textbf{Data availability:} 22 datasets are distributed with the
\texttt{psymetadata} R package (CRAN). We do not use its Many Labs 2
dataset, which we obtain from the original source and include
separately. After excluding Many Labs 2 and separately representing the
intelligence meta-meta-analysis, the remaining psychology datasets vary
from 65 rows of data to over 1,000. The package is GPL-3; individual
datasets originate from the cited source papers.

\textbf{Data processing:} minimal. We used regular expressions to
extract year labels from titles. We dropped some invalid rows (missing,
non-finite, or non-positive standard errors). Signed z-values were
computed as effect sizes divided by their standard errors.

\textbf{Additional grouping variable:} name of the original psymetadata
dataset.

\newpage

\subsection{Askarov et al 2023
(economics)}\label{askarov-et-al-2023-economics}

\textbf{Reference:} \textcite{askarov2023significance}.

\textbf{Research question:} Impact of mandatory data sharing on
(excessive) statistical significance in economics papers

\textbf{Data availability:} file
\texttt{Mandatory\ data-sharing\ 30\ Aug\ 2022.dta} may be downloaded
from
\url{https://github.com/anthonydouc/Datasharing/blob/master/Stata/};
reproducibility package at
\url{https://dataverse.harvard.edu/file.xhtml?fileId=7884702&version=1.0}

\textbf{Data description and source:} The paper includes 64,000 economic
estimates surveyed by Ioannidis et al.~(2017) plus results of
``searching through numerous databases, journal websites, and also an
email survey of 109 authors known to have produced meta-analyses of
economic topics. We cast the widest net possible to capture empirical
economic estimates. Thus, some of the papers included in these
meta-analyses were originally published in political science and
psychology journals. Nevertheless, these meta-studies deal with
economics topics.'' Later they note: ``we collect 166,924 parameter
estimates from 345 distinct research areas, of which 20,121 were
published in 24 of the leading general interest and field journals'' The
paper mentions 12,521 observations before and 2,537 after data sharing
policies in 24 journals; reproducibility dataset has 32 journals
(authors removed some smaller ones) and 22,172 rows. The rows are
meta-analysis estimate rows, not all results from each paper: the
meta-analyses collect comparable effect sizes for specific economic
phenomena and are not used only to identify papers for full extraction.

\textbf{Notes:} Askarov et al article starts from the
Ioannidis-Stanley-Doucouliagos dataset, same as in the case of
Arel-Bundock et al (another dataset in BEAR). Both datasets incorporate
additional data and target different fields of research, but there is
likely a lot of overlap between the two sets.

\textbf{Data processing:} We use the same source file
\texttt{Mandatory\ data-sharing\ 30\ Aug\ 2022.dta} (11.6 MB) as in the
reproducibility package. Signed z-values were computed as reported
effect sizes divided by their standard errors.

\newpage

\subsection{Metapsy (psychotherapy)}\label{metapsy-psychotherapy}

Studies included in \emph{Metapsy} (\url{https://www.metapsy.org/}), a
set of living meta-analytic databases of randomised trials of
psychotherapeutic interventions.

\textbf{Snapshot date:} Jan 2026

\textbf{Data availability:} Metapsy is maintained by an international
collaboration led by Vrije Universiteit Amsterdam. Databases are
available at \url{https://www.metapsy.org/} and via R package
\texttt{metapsyData} \autocite{harrer2022metapsydata}. Metapsy FAQ
states that all data provided as part of the project are open-access and
requires attribution.

\textbf{Data processing:} we merged 20 individual datasets in Metapsy
with some cleaning (e.g.~to extract study dates from titles). Almost all
estimates are Hedges' g, but for one of the databases
(\texttt{total-response}) we converted log-odds ratios to SMD (dividing
by \(\Pi/\sqrt{3}\) to scale SD of logistic regression). Signed z-values
were computed as effect sizes divided by their standard errors.

\newpage

\subsection{Arel-Bundock et al 2022 (political
science)}\label{arel-bundock-et-al-2022-political-science}

\textbf{Reference:} \textcite{arel2022quantitative}.

\textbf{Research question:} assess statistical power in political
science research

\textbf{Data availability:} replication package (zip file with date
20241010) can be found at \url{https://osf.io/fgdet}. All data are in
public domain.

\textbf{Data description and source:} Authors searched for, and
contacted authors of, meta-analysis articles across 141 journals in
political science. The resulting source dataset contains 16,649
hypothesis tests, grouped in 351 meta-analyses and reported in 46
peer-reviewed meta-analytic articles.

\textbf{Notes:} This is a collection of meta-analysis inputs rather than
a direct extraction of all results from primary articles. The source
combines a political-science search with an earlier Doucouliagos work,
meaning that some of this dataset will overlap with Askarov et al.
However, the two articles cover different fields and therefore BEAR
keeps the two datasets separate.

\textbf{Data processing:} using the same code as original authors
(replication package that runs on makefiles), but skipping some
additional processing that they've done for their paper. BEAR uses
\texttt{question\_id} as \texttt{metaid} (351 meta-analysis/research
question groups) Signed z-values were computed as reported estimates
divided by their standard errors. We verified that the distributions of
z-values matched with the article.

\textbf{Additional variables used:} BEAR release includes meta-analytic
article (46 papers). The dataset also includes \texttt{sample} field
records whether a row comes from the Doucouliagos data collection or the
later Briggs/Arel-Bundock data collection.

\newpage

\subsection{Costello and Fox 2022; Yang et al 2023, 2024 (ecology and
evolution)}\label{costello-and-fox-2022-yang-et-al-2023-2024-ecology-and-evolution}

\textbf{Reference:} these two datasets come from the same replication
package and shared data processing pipeline in Yang et al.~2024
\autocite{yang2024large}. Original references for the datasets are Yang
et al.~2023 and Costello and Fox 2022
\autocite{yang2023publication,costello2022decline}.

\textbf{Research question:} decline effects in ecology (Costello and
Fox) and publication bias and performance of empirical research (Yang et
al)

\textbf{Data collection:} Costello and Fox look at 466 meta-analyses
obtained through searching Web of Science. Reproducibility dataset
includes 88,000 rows among 466 analyses in 232 papers. Subsequently,
Yang et al removed duplicated studies and zeroes, which meant discarding
about 20\% of rows. Yang et al collect 102 meta-analyses published
2010-2019 in relevant journals, de-duplicated against Costello and Fox
dataset.

\textbf{Data availability:} two datasets may be downloaded from
\url{https://github.com/Yefeng0920/replication_EcoEvo_git/}. Available
under CC BY 4.0 licence.

\textbf{Data processing:} no additional data processing other than
cleaning up study years. Signed z-values were computed as effect sizes
divided by their standard errors. Note that the replication package for
Yang et al does not include meta-analysis indicators.

\textbf{Additional variables used:} we retained a measure variable
(``lnRR'', ``SMD'', ``Zr'' or ``uncommon'')

\newpage

\subsection{What Works Clearinghouse
(education)}\label{what-works-clearinghouse-education}

Large database of education effect sizes created by Institute of
Education Sciences \autocite{wwc2025studyfindings}.

\textbf{Snapshot date:} 17 May 2025

\textbf{Data availability:} flat files are available at
\url{https://ies.ed.gov/ncee/wwc/studyfindings}. Per permissions and
disclaimers section on that website: ``Unless stated otherwise, all
information on the U.S.\,Department of Education's IES website \ldots{}
is in the public domain and may be reproduced, published, linked to, or
otherwise used without permission from IES.''

\textbf{Data collection:} The WWC source data have 13,054 findings (data
rows) across 1,908 reviews. The dataset includes effect sizes, but not
standard errors, as well as p-values reported by the studies and
p-values re-calculated by the WWC reviewers. After BEAR processing and
filtering, 12,045 findings are retained.

\textbf{Data processing:} We retained only RCTs and quasi-experimental
studies (98\% of data altogether). Where available, we preferred effect
sizes and p-values calculated by WWC to the ones reported by the
studies. We replaced p-values that were equal to zero (this occurred in
3\% of the dataset) with truncated p-value (i.e.~assumed
\(p < 10^{-16}\)). We calculated z-values from these p-values under
assumption of two-sided tests. We then applied the sign of the reported
effect size, so z-values are signed where the effect size is non-zero.

\textbf{Additional grouping variable:} ``outcome domain'' variable
(e.g.~``academic achievement'', ``alphabetics'')

\newpage

\subsection{Cochrane Database of Systematic Reviews
(CDSR)}\label{cochrane-database-of-systematic-reviews-cdsr}

Trials with data available at CDSR,
\url{https://www.cochranelibrary.com/} \autocite{cochrane2025cdsr}

\textbf{Snapshot date:} 20 November 2025

\textbf{Data collection:} using R package \texttt{cochrane}
\autocite{schwab2024cochrane} we merged data from 8,726 records of
reviews in CDSR and merged them into a single file
\texttt{cdsr\_interventions\_19nov2025.csv} (63 MB).

\textbf{Data processing:} minimal processing with extensive filtering.
Final BEAR effect sizes are recalculated for continuous outcomes as
standardised mean differences and for dichotomous outcomes as
probit-transformed effects. Only efficacy outcomes are retained. The
distributed \texttt{BEAR.rds} file includes a smaller analysis subset
with about 38,000 rows: the first comparison and first outcome from each
review, restricted to efficacy outcomes. The processed
\texttt{data/Cochrane.rds} file is larger and is available for users who
want to make different selection decisions. It contains 760,486 result
rows, representing 90,042 review-study pairs across 6,619 Cochrane
reviews.

On processing side, we cleaned up study years, categorised measures
(risk ratio, odds ratio, mean difference etc.) and experimental designs,
especially an ``RCT'' flag (based on scanning of abstracts of each
review for inclusion criteria). Most studies in CDSR are RCTs but some
reviews also allowed quasi-experimental studies, which prevented us from
categorising many studies. We also classify outcome rows into
\texttt{efficacy}, \texttt{safety}, \texttt{dropouts}, and \texttt{bias}
based on the comparison, outcome, and subgroup labels.

Unlike in most of the other datasets in BEAR, we filter CDSR data
heavily. First, we only use the outcome and comparison of each review
that are coded as ``1'', as that is most likely the primary outcome and
most relevant comparison. Secondly, we keep only rows classified as
\texttt{efficacy}, excluding likely safety, dropout, and bias-related
outcomes based on comparison, outcome, and subgroup labels. Thirdly, we
only use studies with continuous and dichotomous outcomes, removing rows
where effect estimates are based on instrumental variables or based on
individual patient data. Lastly, we remove rows where measure of effect
is unknown (retaining: OR, RR, Peto OR, mean difference, standardised
mean difference, and risk difference) and rows where there are zero
subjects.

\textbf{Additional grouping variable:} we retained a ``source data
type'' variable to distinguish estimates from published, unpublished,
``sought'', and mixed data sources. We also retain an
\texttt{outcome\_group} variable in the processed Cochrane data.

\newpage

\subsection{Chavalarias et al.~2016
(PubMed/Medline)}\label{chavalarias-et-al.-2016-pubmedmedline}

\textbf{Reference:} \textcite{chavalarias2016evolution}.

\textbf{Research question:} reporting of p-values in the biomedical
literature

\textbf{Data collection:} the authors used large-scale text mining of
MEDLINE abstracts and PubMed full texts: 4.5mln p-values in 1.6mln
MEDLINE abstracts; 3.4mln p-values in 385k PubMed full-text articles.

\textbf{Data availability:} the extracted p-value dataset is publicly
available
\url{https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/6FMTT3}
(about 6GB of data) As per the hosting platform: this dataset is
released under the Creative Commons Attribution-NonCommercial 4.0
International License.

\textbf{Data processing:} unsigned z-values were derived from p-values
assuming two-sided tests. P-value truncation operators were processed by
collapsing variants such as \texttt{\textless{}\textless{}},
\texttt{\textless{}\textless{}\textless{}}, \texttt{\textless{}=},
\texttt{less\ than}, and \texttt{=\textless{}} into
\texttt{\textless{}}. We dropped 0.7\% of rows where p-values did not
have a ``plain'' format and 0.08\% of rows where truncation could not be
unambiguously classified. For the distributed version of BEAR 50,000
studies are selected at random, with one row per study, in order to keep
the file size manageable.

\textbf{Additional variables used:} source indicator (abstract versus
full text).

\newpage

\subsection{SCORE (social science)}\label{score-social-science}

\textbf{Reference:} \textcite{tyner2026investigating}.

\textbf{Research question:} investigating the replicability of published
claims in the social and behavioural sciences.

\textbf{Data availability:} the SCORE replication package is available
at https://osf.io/g5sny/. The package includes replication data as well
as reviews of claims made in included papers.

\textbf{Data description and source:} BEAR includes two SCORE outputs.
The replications source dataset has 548 rows: 274 original claims and
274 matched replications. After BEAR processing and filtering, 267
matched replication rows are retained. The ``all claims'' source dataset
has 3,066 claim-level rows from the set of replicated papers (but no
replications of these claims), where we select one statistic per claim;
after BEAR processing and filtering, 1,946 claim rows are retained.

\textbf{Data processing:} For the matched replication output, we used
the package's converted correlation scale where available for original
and replication statistics. For the all-claims set, effects are
heterogeneous across the source papers.

When several inputs are available for z-value construction in the
all-claims dataset, we prefer reported z, then reported t, then
coefficient divided by standard error, then signed square-root F for
numerator df 1, then a 95\% confidence interval with a point estimate,
then a two-sided p-value conversion. When the selected statistic only
supplies a p-value and no sign can be inferred, the z-value is unsigned.
For the all-claims text, it is typical to have multiple statistics
backing up a single claim, e.g.~``F(1,38) = 3.73, p = .033, partial
eta-squared = .16; F(1,39) = 7.28, p = .010, partial eta-squared = .16;
F\textless1''. We created a rule to pick one statistic per claim using
agreement with the SCORE significant/nonsignificant coding, statistic
provenance, exactness, available effect and standard error, and text
order.

\textbf{Additional grouping variables:} discipline and SCORE source
indicator.

\newpage

\subsection{Lang 2025 (economics)}\label{lang-2025-economics}

\textbf{Reference:} \textcite{lang2025credible}.

\textbf{Research question:} how frequently are statistically significant
rejections of nulls in economics false positives?

\textbf{Data collection:} This paper uses empirical top-five economics
papers published in 2021 and the Brodeur, Cook, and Heyes dataset of
2015 and 2018 articles in 25 leading economics journals. In each paper,
research assistants checked abstracts and results text, kept estimates
emphasized in abstracts or as principal results, used the authors'
preferred specification when several specifications tested the same
hypothesis, and excluded robustness checks or heterogeneity analyses
unless heterogeneity was central to the article.

The source data contain 3,885 extracted hypothesis tests from 736
papers. The main sample in the Lang paper is the subset of 2,082 tests
with
\texttt{1.96\ \textless{}=\ \textbar{}t\textbar{}\ \textless{}\ 10}. The
paper also reports one null per article: 736 t-values, but without row
or paper identifiers. We do not use the latter.

\textbf{Data processing:} We use the full 3,885-test source table. We
use supplied t-statistics (derounded by Lang) as the \texttt{z} value
and compute two-sided p-values from \texttt{\textbar{}z\textbar{}}. We
add source-article DOIs based on bibliographic metadata matching, and
the reported or derounded coefficients and standard errors. The
one-null-per-article t-vector is not represented in the row-level BEAR
data because its source file has no identifiers that would support
matching to the extracted-test table.

\textbf{Notes:} Presumably there is a strong overlap with Brodeur in
terms of selected papers, but with differences in extracted values.

\newpage

\subsection{Open Science Collaboration 2015
(psychology)}\label{open-science-collaboration-2015-psychology}

\textbf{Reference:}
\textcite{opensciencecollaborationEstimatingReproducibilityPsychological2015a}.

\textbf{Research question:} replications of a quasi-random sample of 100
experiments in psychology.

\textbf{Data collection:} The authors make a comprehensive dataset of
results available with their paper. In BEAR we did not use the original
studies, since all studies in that set have p \textless{} 0.05, only
replications.

\textbf{Data availability:} The data file \texttt{rpp\_data.csv} is
available as part of the repository for the paper
\url{https://osf.io/ytpuq/overview} under a CC0 1.0 Universal license.

\textbf{Data processing:} We derived z-values from the replication
p-values assuming two-sided p-values (we use the replication p-value
column, not the original-study p-value). We applied the sign of the
replication correlation, so z-values are signed where that correlation
is available. We treated p-values recorded as exactly 0 as truncated and
recorded this as a lower bound on z (z-operator
\texttt{\textgreater{}}); otherwise we treated p-values as exact
(z-operator \texttt{=}). We retained the replication sample size as
\texttt{ss}.

\newpage

\subsection{Szucs and Ioannidis 2017 (cognitive
neuroscience)}\label{szucs-and-ioannidis-2017-cognitive-neuroscience}

\textbf{Reference:} \textcite{szucs2017empirical}.

\textbf{Research question:} empirical assessment of published effect
sizes, statistical significance, and power in cognitive neuroscience and
psychology literature.

\textbf{Data availability:} the article and supporting data are
available from PLOS Biology
\url{https://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.2000797}

\textbf{Data description and source:} the source contains 26,841
text-mined t-test records from 3,801 papers in 18 journals (cognitive
neuroscience, psychology, and medical). The processed dataset preserves
all three fields; for BEAR main dataset we include only the cognitive
neuroscience subset (since psychology and medical literature is well
covered by other datasets in BEAR).

\textbf{Notes:} the extraction targeted t-test records reported in
article text and did not mine tables.

\textbf{Data processing:} we followed our default procedure for deriving
z-values from t-values.

\newpage

\subsection{clinicaltrials.gov
snapshot}\label{clinicaltrials.gov-snapshot}

Trials which reported results at clinicaltrials.gov
\autocite{clinicaltrials2025}

\textbf{Snapshot date:} 12 August 2025

\textbf{Data source:} This is a set of flat files of studies obtained
from the AACT downloads page
(\url{https://aact.ctti-clinicaltrials.org/downloads/}; over 2GBs of
data for relevant tables), with relevant columns extracted and joined by
us before BEAR processing.

\textbf{Data availability:} terms and conditions for ClinicalTrials.gov
are at \url{https://clinicaltrials.gov/about-site/terms-conditions}. We
make distributions of derived effect sizes available in accordance with
ToC's. We only use publicly available data and do not imply any
endorsement of this work by National Library of Medicine,
ClinicalTrials.gov or AACT.

\textbf{Data processing:} extensive. We kept only studies where status
was ``Completed'' and only rows of data where outcome type was
``Primary''. We set year to the year of \texttt{completion\_date}.

See \emph{Standard procedure for dealing with p-values and confidence
intervals} for how we created and chose the z-values based on p-values
and confidence intervals. Briefly, we calculated z-values using two
separate procedures (based on p-values and confidence intervals) and, if
both were available, we made a judgement on which one was more
appropriate using a pre-defined rule. ClinicalTrials.gov reports the
number of sides for confidence intervals but not for p-values, so we
treated p-values as two-sided. We dropped rows only when \texttt{z} was
missing. Notably, infinite z-values can arise when \texttt{p\_value} is
recorded as exactly 0, and these are retained because they are not
missing.

\newpage

\subsection{EU Clinical Trials Register (EU
CTR)}\label{eu-clinical-trials-register-eu-ctr}

Trials which reported results at the EU Clinical Trials Register,
\url{https://www.clinicaltrialsregister.eu/} \autocite{euctr2025}.

\textbf{Snapshot date:} 18 January 2026

\textbf{Data collection:} we used R package \texttt{ctrdata}
\autocite{herold2025ctrdata} to create a snapshot of EU CTR
(\texttt{collection\ =\ "euctr"}); we downloaded trial records with
results only. We stored the downloaded records in a local SQLite
database and extracted a fixed set of protocol and results fields plus
several fields computed by \texttt{ctrdata} (trial phase, sample size,
and a ``first primary endpoint'' p-value/size derived by the package).
We only use the EUCTR portion of this extraction in BEAR.

\textbf{Data availability:} EUCTR is publicly accessible. The EUCTR
legal notice notes that publication on EUCTR does not constitute an
endorsement of the information reported.

\textbf{Data processing:} extensive. We use only primary endpoints. We
default missing CI levels to 95\% and where truncation of p-values was
not stated we assume equality (the latter is the case for about 15\% of
data). Where data does not report whether a test is one- or two-sided,
we assume two-sided. Rest of the derivation of z-values follows the\\
\emph{Standard procedure for dealing with p-values and confidence
intervals}. We set \texttt{year} to the entry date year since completion
dates were unavailable. We dropped rows only when \texttt{z} was
missing; infinite z-values are retained. We harmonise phase labels to
follow the same naming convention as ClinicalTrials.gov.

\textbf{Additional variables used:} we retained phase labels and measure
categorical variable (derived by us from the estimand label).

\newpage

\subsection{Barnett and Wren 2019
(PubMed/Medline)}\label{barnett-and-wren-2019-pubmedmedline}

\textbf{Reference:} \textcite{barnett2019examination}.

\textbf{Research question:} Bias for statistical significance in health
and medical journals

\textbf{Data availability:} The dataset Georgescu.Wren.RData may be
downloaded from
\url{https://github.com/agbarnett/intervals/tree/master/data} and also
\url{https://github.com/jdwren/ASEC}. Data file is
\texttt{Georgescu.Wren.RData}. Availability: no clear licence given in
the repo but the article is CC BY 4.0 in BMJ Open.

\textbf{Data description and source:} The dataset is a collection of
confidence intervals for ratio estimates from Medline papers from
1976-2019. Authors scraped (via regular expressions, followed by an
independent check using another data mining algorithm, manual checks for
10,000 intervals) 968,000 CIs from abstracts and 350,000 from full
texts.

\textbf{Notes:} These are ``ratio estimates'' like odds ratios, hazard
ratios and risk ratios. Note that binary outcomes tend to have (much)
lower information than continuous outcomes.

\textbf{Data processing:} We excluded a small fraction of data. First we
restricted to 95\% confidence intervals only: where \texttt{ci.level}
was missing we assumed it was 0.95; among intervals with a known
\texttt{ci.level}, about 0.3\% were not 95\% and were dropped. We
dropped intervals with non-positive width
(i.e.~\texttt{lower\ \textgreater{}=\ upper}). We used log scale (we
replaced zero or negative lower bounds with a small positive constant;
this affected about 0.1\% of the sample) and backed out an approximate
standard error and point estimate under the usual normal approximation
for a 95\% CI, setting point estimate to half-point of the interval.

For the distributed version of BEAR 50,000 studies are selected at
random, with one row per study, in order to keep the file size
manageable.

\newpage

\section{Standard procedure for dealing with p-values and confidence
intervals}\label{standard-procedure-for-dealing-with-p-values-and-confidence-intervals}

Most datasets come with pre-computed effect sizes and standard errors.
Some (especially databases of clinical trials and large sets of scraped
studies) report p-values. Reporting in clinical trial database is done
by investigators and data entry fields are not standardised, requiring
more extensive clean-up and a procedure for deriving z-values.

\subsection{Cleaning up data}\label{cleaning-up-data}

For confidence interval levels, we clean them up by setting values above
100 or below 0 to missing, and treating values below 1 as proportions
rather than percentages by multiplying by 100. This means that, for
example, 0.95 is treated as a 95\% confidence interval. For missing
values in EU CTR database, we assume 95\%.

In clinical trial datasets we classify the effect measure using text
matching to a small set of classes (Mean Difference, Odds Ratio, Risk
Ratio, Hazard Ratio, Geometric Ratio, Risk Difference, Difference in
Percentages, Ratio/Other Ratio, and Other). This string-based mapping is
an arbitrary choice. Unstandardised data in these datasets have many
hundreds of values.

\subsection{Confidence intervals}\label{confidence-intervals}

When working with CIs, ratio measures were analysed on the log scale (if
and only if lower bound, upper bound, and point estimate were all
strictly positive) and non-ratio measures were always kept on the raw
scale.

For z-statistics derived from confidence intervals, we computed the
critical value using stated CI percent and the reported number of sides
(if missing, we defaulted to a two-sided interval). To avoid undefined
critical values (e.g.~when at 100\% or extremely close to it), we
bounded the implied \(\alpha\) at a small value. We then computed two
one-sided standard error estimates from the upper and lower bounds and
used their average when both were finite.

We computed a simple symmetry diagnostic for the confidence interval on
the chosen scale, defined as the smaller of the two half-widths divided
by the larger. We treated intervals as ``symmetric enough'' only if this
ratio exceeded 0.8. This threshold is arbitrary and affects when we
trust the CI-derived z-statistic.

We also flagged potentially non-Wald intervals using text matching on
type of parameter column, if available, searching for keywords such as
median, Hodges, posterior/Bayes, exact, Fieller, bootstrap, and
permutation. Any row flagged this way was treated as unreliable for
CI-based inference, regardless of its numeric properties.

\subsection{p-values}\label{p-values}

The default approach, used for several datasets which report p-values,
especially those scraping data from PubMed/Medline, is to treat p-values
as two-sided, using the upper-tail standard normal quantile
corresponding to \(p/2\). In EU CTR, when the result is marked as
one-sided, we use the corresponding one-sided normal quantile instead;
missing sidedness is treated as two-sided. ClinicalTrials.gov does not
provide a separate p-value sidedness field, so its p-values are treated
as two-sided.

When a source reports t-statistics and degrees of freedom, we first
derive the two-sided p-value from the t distribution as twice the
upper-tail probability beyond the absolute observed t-statistic. We then
store the signed normal-equivalent statistic by applying the sign of the
t-statistic to the upper-tail standard normal quantile corresponding to
half that two-sided p-value.

For clinical trials databases (clinicaltrials.gov and EU CTR) we
sometimes found ambiguity in how p-values were recorded. Sometimes
significant results report p-values close to 1, suggesting that authors
reported cumulative distribution, \(\Phi(z)\). Therefore for each row we
also calculated \(2\cdot\min\{p,1-p\}\). When a CI-derived z-statistic
was available, we chose whichever p-value led to a z-value that was
closest to the CI-derived z.

To avoid dropping rows, we retained unsigned z-statistics when the sign
could not be determined. If the sign of effect was known, we applied it
to the ``p-derived'' z; otherwise we used absolute value.

\subsection{Choice of a single z-value when multiple candidates
available}\label{choice-of-a-single-z-value-when-multiple-candidates-available}

In situations where \(z\) can be derived from both CIs and p-values. We
choose a single ``best'' z-statistic per row as follows. We prefer the
CI-derived \(z\) when it looked like a plausible Wald interval on the
chosen scale, meaning: (1) finite \(z\) and standard error, (2) positive
standard error, (3) not flagged as non-Wald by keyword search in measure
label, and (4) either missing symmetry information or symmetry above
0.8. Otherwise we used the p-derived z.
